Characteristic polynomials of p-adic matrices

### 2017-02-04 charpoly/charpoly.tex

\begin{rem}
As a consequence of the previous discussion, once the optimal jagged 
precision is known, it is possible to lift the entries of $M$ to a sufficiently
large precision and then use 
and then to perform a computation of the characteristic polynomial 
at the optimal precision. This requires $\softO(n^3)$ operations in $K$ 
but, for several instances, may require to increase a lot the precision.
\end{rem}

>>>>

\begin{rem} \label{rem:lift_for_optimal}
As a consequence of the previous discussion, once the optimal jagged 
precision is known, it is possible to lift the entries of $M$ to a sufficiently
large precision, rescale them to have entries in $O_K$
and then use Algorithm 2 to
compute the characteristic polynomial.
The output might then need to be rescaled and
 truncated at the optimal precision. 
This requires $\softO(n^3)$ operations in $O_K$ 
and unfortunately, for several instances, may require to increase a lot the precision.
\end{rem}
